\protect Connecting Every Bit of Knowledge: \\ Wikipedia's First Link Network Unravelled

### 2016-01-03 writeup/2015-11-wikipedia-network.tex
edits to discussion section

\begin{abstract}
  \protect
Apples, oranges, and the most obscure Dylan song too---is every subject a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic though, Wikipedia is a web of naturally emerging relationships.  
By following the First Link in an article, we connect entries to form a directed network: Wikipedia's First Link Network. 
Here we study the English edition of Wikipedia's First Link Network for insight into how the many topics, ideas, people, objects, and events
are related and organized.

@@

We identify the set of First Links directly referencing a particular article 
by studying the indegree of the FLN. 
A higher indegree suggests more authors found the ideas in the article 
pertinent to reference. 
We rank all 11 million articles by indegree to find 
the "United States" with 80,249 direct First Links as the most referenced
Wikipedia article 
(see figure~\ref{fig:ndegree list}). 
Other high-ranking articles
include foundational abstract concepts such as "village," "species,"; 
sports associations such as "American Football," "Association Football"; 
and developed nations such as "France," "Japan," "Russia," "Australia," and 
the "Netherlands." These high ranking articles are useful abstractions: nations
describe a collection of individuals, a common culture, language, or 
geographical proximity; sports teams describe an ever changing collection of 
sports players often associated with a cultural identity and a geographical 
region. Since abstractions such as nations and teams are inherently comprised
of many parts, authors reference the larger abstraction when describing 
a part. For example, in describing the geographical region of north America, 
the United States, Canada, or Mexico are natural references anchoring the 
geographical location to a larger national identity.

"Philosophy" and other philosophical concepts with many traversal visits
are not among the highest-ranking articles by indegree.
"Philosophy" has an indegree of 581, with direct First Links from articles about Philosophers and areas of Philosophy: "Existentialism and Humanism," "Predeterminism," "Synoptic Philosophy,"Qualia," "Dorothy Emmet," and "Christopher W. Morris."
While many articles accumulate at "Philosophy" (see the coming traversal visits discussion), 
the accumulation is not the 
result of many articles directly referencing "Philosophy." 
Instead, the accumulation of First Links, as we argue in our 
discussion of traversal visits, flows towards Philosophy as the 
ultimate anchor when generalizing from specific articles towards broader notions.

@@

The FLN's indegree exhibits a scale-free distribution where a few articles 
receive a most direct first references, while most articles receive few or none.
The average indegree for all 11 million articles is 3.6 direct First Links with a standard deviation of 89.5 links.
Only 4,826 articles have more than 100 direct First Links and $75\%$ of articles
have fewer than 9. 
When fit with a linear model on a log-log scale (log(rank) versus log(indegree)), 
the model's r value is $-0.98$ suggesting a strong log-log linear fit 
with a power law exponent of $-0.79$.

@@

We first seek to describe the depth of the FLN: how many links does a 
connection of ideas span? We gauge the FLN's depth via path length or the number of links traversed until a repeated or invalid link (one outside the FLN). 
We discover the longest path length is 365,
corresponding to the yearly calendar of Orthodox Liturgics.
Each day's Liturgics links to the next day's. On the last calendar day, the last article simply links back to January 1, forming a 365-cycle 
(see discussion of cycles).
We also found similarly lengthy paths following the evolution of a place or topic through time: 
"1953 in Scotland" or "1560s Architecture", with articles sequentially proceeding by year, decade or era.
The longest paths connecting ideas are organized temporally.

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with an interquartile range (26, 30).
The median path length far exceeds the popular 6-degrees of separation (see for 
example the average number of academic publications separating scholars 
\cite{six_degrees}), indicating a greater network depth. 
The network's depth suggests ideas are not related in small independent clusters. 
Instead the many diverse ideas fit together in long-chained connections.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ First Links 
while a few temporally organized paths exceed 50 links 
(see figure~\ref{fig:Path Length Distribution}).

How can we characterize the flow of ideas along a path? Next, we develop 
a metric to gauge the accumulation of First Link references
and characterize a global organization 
of ideas among articles.

@@

We followed every possible path through the network, incrementing
the number of traversal visits for every First Link reference along a path 
to generate a total of 232 million traversal visits.

As a distribution, the number traversal visits per article appears to be scale-free. 
The majority of articles have fewer than 30 traversal visits. 
First Link references accumulate at a few articles.
Specifically, $99.76\%$ of articles have fewer than $100$ traversal visits; nearly $80\%$ have none. 
Meanwhile, the highest ranking 30 articles have an extremely disproportionate number of traversal visits.

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
  }
  We fit the distribution to a linear log-log model by considering the log (base 10) transformed rank of each article against log (base 10) transformed the number of traversal visits. 
  The model explains $86\%$ of the variation in the data, yielding an r-value of $-0.93$ 
  and a power law exponent of $-0.636$. The horizontal flattening around the highest
  ranking articles is a result of the cyclic structure (see discussion on cycles).
  \label{fig:Distribution of Visits}

@@

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
  }
  We compute the number of traversal visits for each article in the FLN (see 
  Traversal Algorithm section for details). In doing so, we can rank each article
  by the accumulation of First Links. Articles with a greater number of traversal visits
  mark greater points of First Link accumulation. The highest ranking articles by traversal visits reveals where the greatest accumulation occurs.
  \label{fig:highest visits}
\end{figure}

@@

The highest ranking articles by traversal visits are 
broad, global topics
(see figure~\ref{fig:highest visits}):
many are academic disciplines such as "Science," "Math," 
"Geography," "Philosophy," "Biology," and "Physics"; others are abstract fundamental concepts such as 
"Community", "State", "Earth", "Information", 
"Existence," "Communication", and "Power."
Since traversal visits measure the accumulation of First Link visits in Wikipedia, 
the highest ranking articles suggest a flow from specific to general. 
For example the flow of First Links for the "Banana" article begins at a very concrete
and specific topic, then flows into progressively broader disciplines, eventually 
culminating at "Philosophy": "Banana" links to the broader category of "Fruit," which then links to 
"Botany," eventually "Biology," then "Science" and ultimately "Philosophy."

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/synonyms.png}
  \caption{
    \textbf{Number of Synonyms for the highest-ranking articles.}
    We use WordNet (the largest lexical database for the English language)
    to identify the number of synonyms for an article's title. We compare 
    the distribution of synonyms of the highest-ranking 100 articles
    against all other Wikipedia articles. As the distribution demonstrates
    the highest ranking concepts have more synonyms than other articles.
  }
  \label{fig:synonyms}
\end{figure}

To measure the specificity of an article, we identify the number of synonyms available for a word or topic. 
A  broader topic likely has many more synonyms relative to a specific, concrete topic. 
Banana has fewer synonyms than botanical for example. 
To quantify the observed flow, we measured the number of synonyms each title contained in WordNet---the largest lexical database of the English language 
\cite{wordnet}. 
We find the highest ranking 100 articles have on average 5 more synonyms than the typical article; a difference of 2.5 synonyms if we compare the median number of synonyms in each group
(see figure~\ref{fig:synonyms}). 
As suggested by the median, many articles have no synonyms as we might expect, because titles with more than one word are not likely to appear in a thesaurus. 
Since many articles have no synonyms, we also compared the number of synonyms in the highest-ranking versus typical article, this time excluding all articles without at least 1 synonym. 
We still find the highest ranking 100 articles with an average of 9.0 (median of 7.0) synonyms whereas the remaining articles have on average 5.8 synonyms (median of 7.0), even with the exclusion of all articles without any synonyms.
The quantifiable difference in synonyms corroborates the flow of links from concrete, specific articles to broader disciplines or fundamental notions.

@@

The recurrence of an exact number of traversal visits suggests some articles are part of a cycle. 
The "Philosophy" article for example sits in what seems like a cycle of seven other articles; "Hypothesis" appears to sit in a 
cycle of 6 other articles including "Experiment", "Fact", and "Knowledge".
To confirm the suggested cyclic structure, we record the history of articles traversed along a path. For example starting on "Train" we construct an path of articles: 
"Rain Transport,"
"Conveyance of Passengers and Goods," 
"Goods," 
"Economics,"
"Social Science,"
"Academic Disciplines,"
"Knowledge,"
"Awareness,"
"Consciousness,"
"Quality,"
"Philosophy."

@@

Similarly, 3-cycles captured a synonymous or close relation among 3 articles: "Tree of life (Biology)", "Tree of life (disambiguation)", 
and "Tree of life"; "Cinema of India", "Indian Cinema", and "Telugu Cinema"
(see figure~\ref{fig:3-cycles}).
Once we extend our cycle size beyond a length of 6 however, 
"Philosophy" along with the remaining list of high ranking articles by traversal visits dominate.

@@

Extending beyond 3-cycles we find the highest ranking cycles of length 
up to 10 links are dominated by "Philosophy," high ranking 3-cycles
around the "Balkans" and "Tree of life" as well as popular 2-cycles.
The longest cycle in the network spans 365 articles of Eastern Orthodox Liturgics for each calendar day.
Other lengthy cycles span 60-75 articles including collections of articles on national histories such as "Japanese Eras" 
or judicial bodies such as the "Legislative Assembly of Ontario".

@@

Ranking articles by the number of traversal funnels we find 
"Philosophy" as by far the highest-ranking article with 
$7.37$ million paths
(see figure~\ref{fig:Funnels}).
\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\textwidth]{graphics/funnels.pdf}
  \caption{
    \textbf{Funnels.}
    We represent the highest-ranking articles by the number of traversal 
    funnels to gauge the influence each article exerts in shaping the 
    structure of the FLN. We find "Philosophy" exerts an overwhelming proportion
    of the influence, with other abstract notions and topical concepts ranking
    next.
  }
  \label{fig:Funnels}
\end{figure*}
Of any article, the number of traversal funnels Philosophy holds exceeds 
all others by more than two orders of magnitude.
The "Philosophy" cycle which contains "Existence," "Awareness," "Reality," 
and similar articles accumulates the overwhelming proportion of its 
references through "Philosophy": $7.37$ million of the $7.4$ million references
are funneled through "Philosophy."
Second on the list of highest-ranking articles by traversal funnels is 
"Presentation" with only $30$ thousand paths. Similarly abstract 
ideas also rank highly such as "Tree of life" (30 thousand), 
"Reality" (13 thousand), "Jurisdiction" (3 thousand) also appear of the list.

Curiously, many high-ranking articles are remarkably topical, culturally and politically important ideas.  For example, "Health Care", a recently high-contested legislative topic appears high on the list---Google trends indicates an uncharacteristic spike in search frequency between August-2009 and February-2010.
Other high ranking articles include key historical events such as the "Cold War" or critical scarce resource with recent 
media discussion such as "Fossil Fuel". 
The highest-ranking list even includes "Hip Hop," "Cancer," and "Web Page."
This coincidence of recent relevance and traversal feed rank suggests the First Link Network measurably represents
meaningful relationships not only among ideas, but also to English-speaking society. 
\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/funnels_distribution.png}
  \caption{
    \textbf{Distribution of Traversal Funnels.}
  We fit the distribution to a linear log-log model by considering the log (base 10) transformed rank of each article against log (base 10) transformed the number of traversal funnels. 
  We find two regimes with the top regime (log(rank) < 4) 
  well-explained by a linear fit, yielding an r-value of $-0.99$ and a 
  power-law exponent of $-1.08$. The top regime 
  explains the distribution of traversal funnels for the $17, 821$ 
  articles with at least one traversal funnel. The bottom 
  horizontal regime corresponds to the more than $99\%$ of articles
  which hold zero traversal funnels.
  }
  \label{fig:Funnels Distribution}
\end{figure}

@@

Wikipedia released an API to measure article popularity by page views
starting November 2015. Page views add another dimension to our
findings by revealing 
how users view the information on Wikipedia. 
We measure popularity as the total number 
of page views in the English edition of Wikipedia in the month of 
October 2015---the earliest full month for which the data is available. 
We find the highest ranking 1000 articles by traversal visits have an average of
$70$ thousand page views in October with high variation: the standard deviation 
is $1.1$ million page views. 
The number of page views has a skewed distribution with $75\%$ of articles
reaching fewer than $73$ thousand page views in October.
The article for "United States" has the most page 
views of the highest ranking $1000$ articles by traversal visits with 
$1.4$ million views in October. The next most popular articles are 
"India," "World War II," and the "United Kingdom" each with $0.7-1.03$ million page views.

The "Philosophy" article despite outranking every article in traversal visits,
has only $240$ thousand page views in October compared to the $1.4$ million
page views for "United States".
While "Philosophy" is not itself the most popular article, "Philosophy" serves as 
an accumulation point for ideas. Wikipedia users do not login specifically
to read about "Philosophy," but the authors relate ideas to "Philosophy" 
by ultimately anchoring the flow of First Links to "Philosophy."

@@

We also analyze article popularity for the highest ranking 1000 articles by 
traversal funnels. In October, the average page views per article is 
$22$ thousand with a standard deviation of $95$ thousand views. The distribution
is skewed with $75\%$ of articles reaching fewer than $20$ thousand page views. 
"Halloween" is the most popular article with $2.8$ million views in October,
likely a result of Halloween falling in the month of October. 
Other popular articles include "Scientology" ($463$ thousand views), "Clint Eastwood" 
($341$ thousand views),
and the "Cold War" ($298$ thousand views) although each has significantly fewer views compared to the views for "Halloween."
Other standout popular October articles include "24-hour" and "12-hour" clocks likely due
to Daylight savings in October and "Marriage" likely due to the drop in the number of
weddings in the months following October
\cite{weddings}.
"Philosophy" which ranks seventh among the most popular of the highest ranking articles by traversal funnels, appears no where in the top 20
by traversal visits. "Philosophy" is a relatively popular article 
among articles influencing the shape of the network, but less popular among 
articles with a large accumulation among the flow of First Links.

>>>>

\begin{abstract}
  \protect
Apples, oranges, and the most obscure Dylan song too---is every topic a few clicks from Philosophy? 
Within Wikipedia, the surprising answer is yes: nearly all 
paths lead to Philosophy.
Wikipedia is the largest, most meticulously indexed collection of human knowledge ever amassed. 
More than information about a topic though, Wikipedia is a web of naturally emerging relationships.  
By following the First Link in an article, we connect entries to form a directed network: Wikipedia's First Link Network. 
Here we study the English edition of Wikipedia's First Link Network for insight into how the many topics, ideas, people, objects, and events
are related and organized.

@@

We identify the set of First Links directly referencing a particular article 
by studying indegree in the FLN.
A higher indegree suggests more authors found the ideas in the article 
pertinent to reference. 
We rank all 11 million articles by indegree to find 
the "United States" with 80,249 direct First Links as the most referenced
Wikipedia article 
(see figure~\ref{fig:ndegree list}). 
Other high-ranking articles
include foundational abstract concepts such as "village," "species,"; 
sports associations such as "American Football," "Association Football"; 
and developed nations such as "France," "Japan," "Russia," "Australia," and 
the "Netherlands." These high ranking articles are useful abstractions: nations
describe a collection of individuals with a common culture, language, or 
geographical proximity; sports teams describe an ever changing collection of 
sports players often associated with a cultural identity or a geographical 
region. 
Since abstractions such as nations and teams are inherently comprised
of many parts, authors reference the abstraction when describing a part.
In describing the New England Patriots or the New York Giants
for example, "American Football" is the natural abstraction, which 
anchors many specific teams.

"Philosophy" and other philosophical concepts
are not among the highest-ranking articles by indegree.
"Philosophy" has an indegree of 581, with direct First Links from articles about Philosophers and areas of Philosophy: "Existentialism and Humanism," "Predeterminism," "Synoptic Philosophy,"Qualia," "Dorothy Emmet," and "Christopher W. Morris."
While many articles accumulate at "Philosophy" (see the coming traversal visits discussion), 
the accumulation is not the 
result of many articles directly referencing "Philosophy." 
Instead, the accumulation of First Links, as we argue in our 
discussion of traversal visits, flows towards Philosophy as the 
ultimate anchor when generalizing from specific articles to broader notions.

@@

The FLN's indegree exhibits a scale-free distribution where a few articles 
receive most direct first references; most articles receive few or none.
The average indegree for all 11 million articles is 3.6 direct First Links with a standard deviation of 89.5 links.
Only 4,826 articles have more than 100 direct First Links and $75\%$ of articles
have fewer than 9. 
When fit with a linear model on a log-log scale (log(rank) versus log(indegree)), 
the model's r value is $-0.98$ suggesting a strong log-log linear fit 
with a power law exponent of $-0.79$.\\

@@

We first seek to describe the depth of the FLN: how many links does a 
connection of ideas span? We gauge the FLN's depth by 
measuring path length or the number of links traversed until a repeated or invalid link (one outside the FLN). 
We discover the longest path length is 365,
corresponding to the yearly calendar of Orthodox Liturgics.
Each day's Liturgics links to the next day's. On the last calendar day, the last article simply links back to January 1, forming a 365-cycle 
(see discussion of cycles).
We also find similarly lengthy paths following the evolution of a place or topic through time: 
"1953 in Scotland" or "1560s Architecture", with articles sequentially proceeding by year, decade or era.
The longest paths connect temporally organized ideas.

@@

Of the 11 million articles, 5.5 million had an invalid link or linked back to the same article, yielding a path length of zero. 
This roughly corresponds to the official number of articles on Wikipedia: 
$~4.7$ million as of November 2014---approximately half of the 11 million 
articles in the XML dump are redirects or disambiguations, not full articles.
The most common path length is 29, with an interquartile range of 4---path length
is typically between 26 and 29 articles.
The median path length far exceeds the popular 6-degrees of separation (see for 
example the average number of academic publications separating scholars 
\cite{six_degrees}), indicating a greater network depth.
The network's depth suggests ideas are not related in small independent clusters. 
Instead the many diverse ideas fit together in long-chained connections.
As a distribution, more than $75\%$ of articles have a path length below 
$50$ First Links 
while a few temporally organized paths exceed 50 links 
(see figure~\ref{fig:Path Length Distribution}).

How can we characterize the flow of ideas along a path? Next, we develop 
a metric to gauge the accumulation of First Link references
and describe a pattern for how ideas flow through the FLN.

@@

We follow every possible path through the network, incrementing
the number of traversal visits for every First Link reference.
We generate a total of 232 million traversal visits.

As a distribution, the number traversal visits by article appears to be scale-free. 
The majority of articles have fewer than 30 traversal visits. 
First Link references accumulate at a few articles.
Specifically, $99.76\%$ of articles have fewer than $100$ traversal visits; nearly $80\%$ have none. 
Meanwhile, the highest ranking 30 articles have an extremely disproportionate number of traversal visits.

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/traversals_per_article.png} 
  \caption{
    \textbf{Distribution of Traversal Visits.}
  }
  We fit the distribution to a linear log-log model by considering the log (base 10) transformed rank of each article against log (base 10) transformed the number of traversal visits. 
  The model explains $86\%$ of the variation in the data, yielding an r-value of $-0.93$ 
  and a power law exponent of $-0.64$. The horizontal flattening around the highest
  ranking articles is a result of the cyclic structure (see discussion on cycles).
  \label{fig:Distribution of Visits}

@@

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/articles_ranked.png}
  \caption{
    \textbf{Highest ranking articles by number of traversal visits.}
  }
  We compute the number of traversal visits for each article in the FLN (see 
  Traversal Algorithm section for details). In doing so, we can rank each article
  by the accumulation of First Links. Articles with a greater number of traversal visits
  mark greater points of First Link accumulation. The highest ranking articles by traversal visits reveal where the greatest accumulation occurs.
  \label{fig:highest visits}
\end{figure}

@@

The highest ranking articles by traversal visits are 
broad, global topics
(see figure~\ref{fig:highest visits}):
many are academic disciplines such as "Science," "Math," 
"Geography," "Philosophy," "Biology," and "Physics"; others are abstract fundamental concepts such as 
"Community", "State", "Earth", "Information", 
"Existence," "Communication", and "Power."
Since traversal visits measure the accumulation of First Link visits in Wikipedia, 
the highest ranking articles suggest First Links flow from specific to general articles. 
For example the flow of First Links for the "Banana" article begins at a very concrete
and specific topic, then flows towards progressively broader disciplines, eventually 
culminating at "Philosophy": "Banana" links to the broader category of "Fruit," which then links to 
"Botany," eventually "Biology," then "Science" and ultimately "Philosophy."

\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/synonyms.png}
  \caption{
    \textbf{Number of Synonyms for the highest-ranking articles.}
    We use WordNet (the largest lexical database for the English language)
    to identify the number of synonyms for an article's title. We compare 
    the distribution of synonyms of the highest-ranking 100 articles
    against all other Wikipedia articles (with the top 100 articles removed). As the distribution demonstrates
    the highest ranking concepts have more synonyms than other articles.
  }
  \label{fig:synonyms}
\end{figure}

To measure the specificity of an article, we identify the number of synonyms available for a word or topic. 
A  broader topic likely has many more synonyms relative to a specific, concrete topic. 
Banana has fewer synonyms than botanical for example. 
To quantify the observed flow, we measured the number of synonyms each title contained in WordNet---the largest lexical database of the English language 
\cite{wordnet}. 
We compare the highest ranking 100 articles against the all other Wikipedia articles, with the top 100 articles removed.
We find the highest ranking 100 articles have on average 5 more synonyms than the typical article; a difference of 2.5 synonyms if we compare the median number of synonyms in each group
(see figure~\ref{fig:synonyms}). 
As suggested by the median, many articles have no synonyms as we might expect, because titles with more than one word are not likely to appear in a thesaurus.

Since many articles have no synonyms, we also compare the number of synonyms for the highest-ranking versus typical article, this time excluding all articles without at least 1 synonym. 
We still find the highest ranking 100 articles have on average 9.0 
(median of 7.0) synonyms whereas the remaining articles have 
on average 5.8 synonyms (median of 3.0)---even when all articles without
synonyms are excluded.
The quantifiable difference in synonyms corroborates the flow of links from concrete, specific articles to broader disciplines or fundamental notions.

@@

The recurrence of an exact number of traversal visits suggests some articles are part of a cycle. 
The "Philosophy" article for example sits in what seems like a cycle of seven other articles; "Hypothesis" appears to sit in a 
cycle of 6 other articles including "Experiment", "Fact", and "Knowledge".
To confirm the suggested cyclic structure, we record the history of articles traversed along a path. For example starting on "Train" we construct a path of articles: 
"Rain Transport,"
"Conveyance of Passengers and Goods," 
"Goods," 
"Economics,"
"Social Science,"
"Academic Disciplines,"
"Knowledge,"
"Awareness,"
"Consciousness,"
"Quality,"
"Philosophy," and so on until an article is repeated.

@@

Similarly, 3-cycles capture a synonymous or close relation among 3 articles: "Tree of life (Biology)", "Tree of life (disambiguation)", 
and "Tree of life"; "Cinema of India", "Indian Cinema", and "Telugu Cinema"
(see figure~\ref{fig:3-cycles}).
Once we extend our cycle size beyond a length of 6 however, 
"Philosophy" along with the remaining list of high ranking articles by traversal visits dominate.
The longest cycle in the network spans 365 articles of Eastern Orthodox Liturgics for each calendar day.
Other lengthy cycles span 60-75 articles including collections of articles on national histories such as "Japanese Eras" 
or judicial bodies such as the "Legislative Assembly of Ontario".

@@

@@

Ranking articles by the number of traversal funnels we find 
"Philosophy" as by far the highest-ranking article with 
$7.37$ million paths
(see figure~\ref{fig:Funnels}).
\begin{figure*}[tp!]
  \centering	
  \includegraphics[width=\textwidth]{graphics/funnels.pdf}
  \caption{
    \textbf{Funnels.}
    We represent the highest-ranking articles by the number of traversal 
    funnels to gauge the influence each article exerts in shaping the 
    structure of the FLN. We find "Philosophy" exerts an overwhelming proportion
    of the influence, with other abstract notions and topical concepts ranking
    next.
  }
  \label{fig:Funnels}
\end{figure*}
Of any article, the number of traversal funnels Philosophy holds exceeds 
all others by more than two orders of magnitude.
The "Philosophy" cycle which contains "Existence," "Awareness," "Reality," 
and similar articles accumulates the overwhelming proportion of its 
references through "Philosophy": $7.37$ million of the $7.4$ million references
are funneled through "Philosophy."
Second on the list of highest-ranking articles by traversal funnels is 
"Presentation" with only $30$ thousand paths. Similarly abstract 
ideas also rank highly such as "Tree of life" (30 thousand), 
"Reality" (13 thousand), and "Jurisdiction" (3 thousand).

Many high-ranking articles are remarkably topical, culturally and politically important ideas.  For example, "Health Care", a recently high-contested legislative topic appears high on the list---Google trends indicates an uncharacteristic spike in search frequency between August-2009 and February-2010.
Other high ranking articles include key historical events such as the "Cold War" or critical scarce resource with recent 
media discussion such as "Fossil Fuel". 
The highest-ranking list even includes "Hip Hop," "Cancer," and "Web Page."
This coincidence of recent relevance and traversal funnel rank suggests the First Link Network measurably represents
meaningful relationships not only among ideas, but also to English-speaking society. 
\begin{figure}[tp!]
  \centering	
  \includegraphics[width=\columnwidth]{graphics/funnels_distribution.png}
  \caption{
    \textbf{Distribution of Traversal Funnels.}
  We fit the distribution with a linear log-log model by considering the log (base 10) transformed rank of each article against log (base 10) transformed the number of traversal funnels. 
  We find two regimes with the top regime (log(rank) < 4) 
  well-explained by a linear fit, yielding an r-value of $-0.99$ and a 
  power-law exponent of $-1.08$. The top regime 
  explains the distribution of traversal funnels for the $17, 821$ 
  articles with at least one traversal funnel. The bottom 
  horizontal regime corresponds to the more than $99\%$ of articles
  which hold zero traversal funnels.
  }
  \label{fig:Funnels Distribution}
\end{figure}

@@

Wikipedia released an API to measure article popularity by page views
starting November 2015. Page views add another dimension to our
findings by revealing 
how users view the information on Wikipedia. 
We measure popularity as the total number 
of page views in the English edition of Wikipedia in the month of 
October 2015---the earliest full month for which the data is available. 
We find the highest ranking 1000 articles (by traversal visits) have an average of
$70$ thousand page views in October with high variation: the standard deviation 
is $1.1$ million page views. 
The number of page views has a skewed distribution with $75\%$ of articles
reaching fewer than $73$ thousand page views in October.
The article for "United States" has the most page 
views of the highest ranking $1000$ articles by traversal visits with 
$1.4$ million views in October. The next most popular articles are 
"India," "World War II," and the "United Kingdom" each with $0.7-1.03$ million page views.

The "Philosophy" article despite outranking every article by traversal visits,
has only $240$ thousand page views in October compared to the $1.4$ million
page views for "United States".
While "Philosophy" is not itself the most popular article, "Philosophy" serves as 
an accumulation point for ideas. Wikipedia users do not login specifically
to read about "Philosophy," but the authors relate ideas to "Philosophy" 
by ultimately anchoring the flow of First Links to "Philosophy."

@@

We also analyze article popularity for the highest ranking 1000 articles by 
traversal funnels. In October, the average page views per article is 
$22$ thousand with a standard deviation of $95$ thousand views. The distribution
is skewed with $75\%$ of articles reaching fewer than $20$ thousand page views. 
"Halloween" is the most popular article with $2.8$ million views in October,
likely a result of Halloween falling in the month of October. 
Other popular articles include "Scientology" ($463$ thousand views), "Clint Eastwood" 
($341$ thousand views),
and the "Cold War" ($298$ thousand views) although each has significantly fewer views compared to the views for "Halloween."
Other standout popular October articles include "24-hour" and "12-hour" clocks likely due
to Daylight savings in October and "Marriage" likely due to the drop in the number of
weddings in the months following October
\cite{weddings}.
"Philosophy" which ranks seventh among the most popular of the highest ranking articles by traversal funnels, appears no where in the top 20
by traversal visits. "Philosophy" is a relatively popular article 
among articles influencing the shape of the network, but less popular among 
highly-ranked articles by accumulation.
